The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey

### 2020-03-19 RET_Hosts_IR.tex

\subsection{Spectroscopy \label{subsec:spec}}
Accurate redshifts for DES-SN were obtained by OzDES, a dedicated DES spectroscopic follow-up campaign based at the $3.9~\textrm{m}$ Anglo-Australian Telescope (AAT) using the AAOmega fibre-fed spectrograph and 2dF fibre positioner. The observation strategy of OzDES was to point at one of the ten DES-SN fields, and place fibres at the positions of transient hosts, continually coadding the spectra of a particular host until a redshift was obtained at which point the fibre could be allocated to a different transient. The spectra have a resolution of 1400-1700 and a wavelength range of $3700~8800$~\AA, and are reduced using the OzDES pipeline which makes use of a modified version of v6.46 of the 2dfdr \citep{Croom2004} along with internal scripts. \replychris{We use internal data release 7, a preliminary version of the public data release is detailed in \citet{Lidman2020}.} Extensive description and discussion of OzDES can be found in \citet{Yuan2015,Childress2017,Lidman2020}. \replychris{We also obtained redshifts for some transient hosts serendipitously as part of the Looking at the Distant Universe with the MeerKAT Array (LADUMA) survey\footnote{\url{http://www.laduma.uct.ac.za}}, three of which are present in our sample} .
Objects for which the host already had a publicly available redshift were not observed with OzDES, but merged into the GRC nontheless.  Where the spectra from which those redshifts were derived are also public they are included in this analysis. These comprise the Galaxy and Mass Assembly survey (GAMA \citealt{Driver2009,Baldry2018}) and SDSS. In total we analyse 42 spectra, with a mean continuum signal-to-noise ratio (SNR) of 2.56/pixel. We stress that the emission lines are detected with a higher SNR than this.

@@

To estimate parameters from the OzDES host galaxy spectra requires several processing steps. We first apply a flux calibration by `mangling' the spectrum such that the integrated flux over the wavelength ranges of the DES photometric bands matches that measured in the photometry (further details on the mangling process are provided in \citealt{Swann2020}). We use a circular aperture of diameter 2\arcsec, matching the size of the spectrograph fibres. \replylluis{This way the resulting spectrum is a more accurate representation of the true spectrum at that point in the galaxy. This only holds, however, for the area covered by the fibre and we note that the resulting spectrum is not necessarily representative of the galaxy as a whole. There are several reasons this may not be the case, such as metallicity and age gradients or structure such as bars and discs (see e.g. \citealt{Iglesias-Paramo2013,Iglesias-Paramo2016}), and proceed with our analysis with this caveat acknowledged.}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/SFR_Mike.png}
\caption{The $M_*$ - SFR sequence of RET hosts, \phil{hosts of other transients, and SDSS field galaxies. Transient SFRs have not been corrected for redshift evolution. RET hosts lie slightly above the low-$z$ star-formation main sequence.}
\label{fig:sfms_sfr}}
\end{figure}

@@

The most common method used to estimate the metallicity of galaxies is to use emission line ratios that have been calibrated using theoretical or empirical models in order to approximate the gas-phase oxygen abundance in the interstellar medium. Emission lines originate from regions of ionised gas, but there are a number of possible causes of this ionisation. Using the Baldwin-Phillips-Terlevich diagram (Fig. \ref{fig:bpt}; \citealt{Baldwin1981}), we demonstrate that the emission line ratios measured in RET hosts are consistent with ionisation caused by star-formation as opposed to AGN. \replylluis{We note than only 11 of the 44 RET host spectra have the necessary lines to plot a BPT diagram. This is also the case for the \SII and \OI versions of the diagram, and we find no evidence AGN amongst the 12 hosts in those diagrams either.}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/sSFR_Mike.png}
\caption{The sSFR of RET hosts and comparison samples, along with the SDSS field galaxies.
\label{fig:sfms_ssfr}}
\end{figure}

@@

We show the cumulative distribution of sSFR in Fig.~\ref{fig:ssfr_cum}. The RET hosts are clearly shifted to higher sSFRs than CCSNe. To statistically compare the host sSFR distribution of RETs with the other samples, we employ the method of \citet{Wiseman2020}. For each pair of samples, we model the PDFs as skewed normal distributions \replylluis{described by the parameters `loc' (location, identical to mean \replychris{for zero skewness}), `scale' (spread, identical to standard deviation for \replychris{zero skewness})\footnote{See \citet{Wiseman2020} for a detailed description of the fitting procedure and the parameters describing the skewed normal distributions}, and `skewness'. To impose priors on loc and scale, we combine the two samples and use normal priors centered on the combined mean and twice the combined standard deviation respectively, while for skewness the prior is a broad normal distribution centered on 0. We note that the loc parameter describes the location of the distribution (its relative position on the x-axis) and is not a mean, median, or mode. A highly-skewed distribution may have a loc that lies above almost the entire sample. A worked example as well as} the results from the simultaneous fitting are displayed in Appendix \ref{app:b}.

>>>>

\subsection{Spectroscopy \label{subsec:spec}}
Accurate redshifts for DES-SN were obtained by OzDES, a dedicated DES spectroscopic follow-up campaign based at the $3.9~\textrm{m}$ Anglo-Australian Telescope (AAT) using the AAOmega fibre-fed spectrograph and 2dF fibre positioner. The observation strategy of OzDES was to point at one of the ten DES-SN fields, and place fibres at the positions of transient hosts, continually coadding the spectra of a particular host until a redshift was obtained at which point the fibre could be allocated to a different transient. The spectra have a resolution of 1400-1700 and a wavelength range of $3700~8800$~\AA, and are reduced using the OzDES pipeline which makes use of a modified version of v6.46 of the 2dfdr \citep{Croom2004} along with internal scripts. \replychris{We use internal data release 7, a preliminary version of the public data release which is detailed in \citet{Lidman2020}.} Extensive description and discussion of OzDES can be found in \citet{Yuan2015,Childress2017,Lidman2020}. \replychris{We also obtained redshifts for some transient hosts serendipitously as part of the Looking at the Distant Universe with the MeerKAT Array (LADUMA) survey\footnote{\url{http://www.laduma.uct.ac.za}}, three of which are present in our sample} .
Objects for which the host already had a publicly available redshift were not observed with OzDES, but merged into the GRC nontheless.  Where the spectra from which those redshifts were derived are also public they are included in this analysis. These comprise the Galaxy and Mass Assembly survey (GAMA \citealt{Driver2009,Baldry2018}) and SDSS. In total we analyse 42 spectra, with a mean continuum signal-to-noise ratio (SNR) of 2.56/pixel. We stress that the emission lines are detected with a higher SNR than this.

@@

To estimate parameters from the OzDES host galaxy spectra requires several processing steps. We first apply a flux calibration by `mangling' the spectrum such that the integrated flux over the wavelength ranges of the DES photometric bands matches that measured in the photometry (further details on the mangling process are provided in \citealt{Swann2020}). We use a circular aperture of diameter 2\arcsec, matching the size of the spectrograph fibres. \replylluis{This way the resulting spectrum is a more accurate representation of the true spectrum at that point in the galaxy. This only holds, however, for the area covered by the fibre and we note that the resulting spectrum is not necessarily representative of the galaxy as a whole. There are several reasons this measurement may differ from one made at the SN explosion site, such as metallicity and age gradients or structure such as bars and discs (see e.g. \citealt{Iglesias-Paramo2013,Iglesias-Paramo2016}). We proceed with our analysis with this caveat acknowledged.}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/SFR_Mike.png}
\caption{The $M_*$ - SFR sequence of RET hosts, \phil{hosts of other transients, and SDSS field galaxies. SFRs have not been corrected for redshift evolution. RET hosts lie slightly above the low-$z$ star-formation main sequence.}
\label{fig:sfms_sfr}}
\end{figure}

@@

The most common method used to estimate the metallicity of galaxies is to use emission line ratios that have been calibrated using theoretical or empirical models in order to approximate the gas-phase oxygen abundance in the interstellar medium. Emission lines originate from regions of ionised gas, but there are a number of possible causes of this ionisation. Using the Baldwin-Phillips-Terlevich diagram (Fig. \ref{fig:bpt}; \citealt{Baldwin1981}), we demonstrate that the emission line ratios measured in RET hosts are consistent with ionisation caused by star-formation as opposed to AGN. \replylluis{We note than only 11 of the 44 RET host spectra have the necessary lines to plot a BPT diagram. This is also the case for the \SII~and \OI~versions of the diagram, and we find no evidence AGN amongst the 11 hosts in those diagrams either.}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/sSFR_Mike.png}
\caption{The $M_*$ - sSFR sequence of RET hosts and comparison samples, along with the SDSS field galaxies.
\label{fig:sfms_ssfr}}
\end{figure}

@@

We show the cumulative distribution of sSFR in Fig.~\ref{fig:ssfr_cum}. The RET hosts are clearly shifted to higher sSFRs than CCSNe. To statistically compare the host sSFR distribution of RETs with the other samples, we employ the method of \citet{Wiseman2020}. For each pair of samples, we model the PDFs as skewed normal distributions \replylluis{described by the parameters `loc' (location, identical to mean \replychris{for zero skewness}), `scale' (spread, identical to standard deviation for \replychris{zero skewness})\footnote{See \citet{Wiseman2020} for a detailed description of the fitting procedure and the parameters describing the skewed normal distributions.}, and `skewness'. To impose priors on loc and scale, we combine the two samples and use normal priors centered on the combined mean and twice the combined standard deviation respectively, while for skewness the prior is a broad normal distribution centered on 0. We note that the loc parameter describes the location of the distribution (its relative position on the x-axis) and is not a mean, median, or mode. A highly-skewed distribution may have a loc that lies above almost the entire sample. \replychris{A worked example as well as} the results from the simultaneous fitting are displayed in Appendix \ref{app:b}. }
